Hypertension and microbiome

### 2019-10-18 articletwo.Rmd
Comparing how number of associations are changed in deseq

@@

```{r talbe alpha div min}
diversities %>%
    map_df(., ~as.data.frame(.x), .id = "covariates") %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

@@

>>>>

```{r comparing deseq2}
if (!file.exists("rds/dds3.rds")) {
    pseq.genus.core.deseq <-  prune_taxa(taxa(pseq.genus.core), pseq.genus)
    dds3 <- lapply(deseq.list(var.CL, var.CL.min), function(x, dds) {
        dds.data <- phyloseq_to_deseq2(dds, deseq.formula(x, "HYPERTENSION"))
        DESeq(dds.data,
              test="Wald",
              fitType="parametric",
              parallel = TRUE,
              BPPARAM=MulticoreParam(16))}, dds = pseq.genus.core.deseq)
    saveRDS(dds3, file = "rds/dds3.rds")
} else {
    dds3 <- readRDS(file = "rds/dds3.rds")
}
```

@@

```{r talbe alpha div min}
diversities %>%
    map_df(~as.data.frame(.x), .id = "covariates") %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

@@

Comparing how adding additional covariate to basic model for age, sex,
and hypertension changes number of significant associations found for
hypertension.

```{r results compare deseq2}
map(dds3, ~sum(results(.x, name = "HYPERTENSION_1_vs_0")$padj < 0.05)) %>%
    map_df(~as.data.frame(.x) %>% dplyr::rename(qval = .x), .id = "included") %>%
    kable
```
